### 2017-12-30 Paper/examples.tex
work in progress

As mentioned earlier in this section, cheap function evaluations of the discharge using 
Eq.~\ref{eq:bore} enable us to compute converged estimates of $\mathcal{T}(\theta_i)$. Plotted in
Figure~\ref{fig:sense_bore} are estimates of these indices corresponding to the uncertain
parameters in the borehole function using 10$^6$ pseudo-random
samples in the input parameter domain. These estimates are used to verify fidelity of
parameter screening based on the methodology presented in Section~\ref{sec:method}. 
In Figure~\ref{fig:screen_bore}, we plot estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$)
for a wide range of the number of samples used for approximating $\mu_i$ using Eq.~\ref{eq:mu}.
Estimates for $\hat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$
even when small number of samples are used to estimate the expectation in Eq.~\ref{eq:mu}. 
Consequently, the relative importance of uncertain 
parameters in the borehole function is found to be consistent with predictions based on the Sobol' index.

>>>>

As mentioned earlier in this section, cheap function evaluations of the discharge using 
Eq.~\ref{eq:bore} enable us to compute converged estimates of $\mathcal{T}(\theta_i)$. Plotted in
Figure~\ref{fig:sense_bore} are estimates of these indices corresponding to the uncertain
parameters in the borehole function using 10$^6$ pseudo-random
samples in the input parameter domain. These estimates are used to verify fidelity of
parameter screening based on the methodology presented in Section~\ref{sec:method}. 
In Figure~\ref{fig:screen_bore}, we plot estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$)
for a wide range of the number of samples used for approximating $\mu_i$ using Eq.~\ref{eq:mu}.
Estimates for $\hat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$
even when small number of samples (5 -- 10) are used to estimate the expectation in Eq.~\ref{eq:mu}. 
Consequently, the relative importance of uncertain 
parameters in the borehole function is found to be consistent with predictions based on the Sobol' index. 
In the considered intervals for the uncertain parameters, it is clear that the discharge is insensitive to
$T_u$ and $T_l$. Moreover, the sensitivity towards $K_w$ is also small. We exploit this result by 
discounting the uncertainties in $T_u$, $T_l$, and $K_w$ while using nominal values for these
parameters instead.
